---
title: "Getting Started"
author: "Steven M. Mortimer"
date: "2019-05-18"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN
)
```

First, load the **rdynamicscrm** package and authenticate.

```{r auth, include = FALSE}
library(rdynamicscrm)
rdynamicscrm_setup <- readRDS(here::here("tests", "testthat", "rdynamicscrm_setup.rds"))
suppressMessages(dyn_auth(url = rdynamicscrm_setup$url, 
                          username = rdynamicscrm_setup$username, 
                          password = rdynamicscrm_setup$password))
```

```{r load-package, eval=FALSE}
library(rdynamicscrm)
dyn_auth(url = "https://test.ztcrm.org/",
         username = "test@live.com", 
         password = "{PASSWORD_HERE}")
```

The `dyn_auth()` function will obtain a cipher and secret key that will be embedded 
in the header of each SOAP API call to securely access the CRM instance. After obtaining 
these authentication credentials, you can check your connectivity by looking at 
the information returned about the current user. It should be information about you!

```{r}
# pull down information of person logged in
# it's a simple easy call to get started 
# and confirm a connection to the APIs
me <- dyn_whoami()
my_info <- dyn_retrieve(me$UserId, entity_name = "systemuser", 
                        all_attributes = TRUE)
sprintf("Disabled?: %s", my_info$isdisabled)
```

### Create

MS Dynamics CRM has entities and those entities contain records. One default entity is the 
"contact" entity. This example shows how to create two records in the contact entity.

```{r create-records}
n <- 2
new_contacts <- tibble(firstname = rep("Test", n),
                       lastname = paste0("Contact-Create-", 1:n))
created_records <- dyn_create(new_contacts, entity_name="contact")
created_records
```

### Query

MS Dynamics CRM has proprietary form of SQL called FetchXML. FetchXML is a powerful 
tool that allows you to return the attributes of records on almost any entity in 
MS Dynamics CRM including accounts, contacts, custom entities and more! 

For simple "SELECT" queries you only need to specify the entity and the fields.

```{r query-records-1}
queried_records <- dyn_query(entity_name = "contact",
                             attributes = c("modifiedon", "donotbulkemail"), top=3)
queried_records
```

Below is an example where we grab the two contact records we just created using 
FetchXML to specifically target those records.

```{r query-records-2}
my_fetchxml <- '<fetch version="1.0" output-format="xml-platform" mapping="logical" distinct="false">
                  <entity name="contact" >
                    <attribute name="firstname" />
                    <attribute name="lastname" />
                    <filter type="or">
                      <condition attribute="lastname" operator="eq" value="Contact-Create-1" />
                      <condition attribute="lastname" operator="eq" value="Contact-Create-2" />
                    </filter>
                  </entity>
                </fetch>'  
queried_records <- dyn_query(fetchxml = my_fetchxml)
queried_records
```

### Update

After creating records you can update them using `dyn_update()`. Updating a record 
requires you to pass the MS Dynamics CRM `Id` of the record. MS Dynamics CRM creates 
a GUID (globally unique identifier) on each record and uses that to know which record to 
attach the update information you provide. Simply include a field or column in your 
update dataset called "Id" and the information will be matched. Here is an example 
where we update each of the records we created earlier with a new first name 
called "TestTest".

```{r update-records}
# Update some of those records
queried_records <- queried_records %>%
  mutate(firstname = "TestTest") %>% 
  rename(id=contactid)

updated_records <- dyn_update(queried_records, entity_name="contact")
updated_records
```

### Delete

Records can easily be deleted individually or in bulk by passing a vector of IDs 
to the `dyn_delete()` function. Here we will delete the two records that we created 
in this example.

```{r delete-records}
ids_to_delete <- updated_records$id
deleted_records <- dyn_delete(ids_to_delete, entity_name="contact")
deleted_records
```
