---
title: "Getting Started"
author: "Steven M. Mortimer"
date: "2018-08-11"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

First, load the **rdynamicscrm** package and authenticate.

```{r auth, include = FALSE}
suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(here)))
library(rdynamicscrm)
rdynamicscrm_setup <- readRDS(here::here("tests", "testthat", "rdynamicscrm_setup.rds"))
suppressMessages(dyn_auth(url = rdynamicscrm_setup$url, 
                          username = rdynamicscrm_setup$username, 
                          password = rdynamicscrm_setup$password))
```

```{r load-package, eval=FALSE}
suppressWarnings(suppressMessages(library(dplyr)))
library(rdynamicscrm)
dyn_auth(url = "https://test.ztcrm.org/",
         username = "test@live.com", 
         password = "{PASSWORD_HERE}")
```

After authenticating you can check your connectivity by looking at the information 
returned about the current user. It should be information about you!

```{r}
# pull down information of person logged in
# it's a simple easy call to get started 
# and confirm a connection to the APIs
user_info <- dyn_whoami()
sprintf("Name: %s %s", user_info$firstname, user_info$lastname)
sprintf("User Active?: %s", user_info$isactive)
```

### Create

MS Dynamics CRM has entities and those entities contain records. One default entity is the 
"Account" entity. This example shows how to create two records in the Account entity.

```{r create-records}
n <- 2
new_accounts <- tibble(FirstName = rep("Test", n),
                       LastName = paste0("Account-Create-", 1:n))
created_records <- dyn_create(new_accounts, entity_name="Account")
created_records
```

### Query

MS Dynamics CRM has proprietary form of SQL called FetchXML. FetchXML is a powerful 
tool that allows you to return the attributes of records on almost any entity in 
MS Dynamics CRM including Accounts, Contacts, custom entities and more! Below is an 
example where we grab the two Account records we just created.

```{r query-records}
queried_records <- dyn_query(entity - "account")
queried_records

# example using raw FetchXML
queried_records <- dyn_query(fetchxml = my_fetchxml)
queried_records
```

### Update

After creating records you can update them using `dyn_update()`. Updating a record 
requires you to pass the MS Dynamics CRM `Id` of the record. MS Dynamics CRM creates 
a GUID (globally unique identifier) on each record and uses that to know which record to 
attach the update information you provide. Simply include a field or column in your 
update dataset called "Id" and the information will be matched. Here is an example 
where we update each of the records we created earlier with a new first name 
called "TestTest".

```{r update-records}
# Update some of those records
queried_records <- queried_records %>%
  mutate(FirstName = "TestTest") %>% 
  select(-Account)

updated_records <- dyn_update(queried_records, entity_name="account")
updated_records
```

### Delete

Records can easily be deleted individually or in bulk by passing a vector of IDs 
to the `dyn_delete()` function. Here we will delete the two records that we created 
in this example.

```{r delete-records}
deleted_records <- dyn_delete(updated_records$id)
deleted_records
```
